---
title: "Locate Hospitals in Paris"
author: "Edouard"
date: "03/08/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(geosphere)
library(leaflet)
```

## Overall goal of our app
We'd like to build a system locating the closest hospital for habitants of Paris.  

Our app should be able to :  
- Let the user indicate its longitude and latitude coordinates  
- Locate the closest hospital  
- Estimate the time to arrival based on the user's speed  

## Methodology

### 1/ Create Data
First, let's build a list of the 12 largest hospitals in inner Paris.

```{r data, echo = FALSE}
hospitals <- data.frame(
name = c("Salpetriere", "Bichat", "Robert-Debre", "Lariboisiere",
         "Georges-Pompidou","Necker","Cochin","Armand-Trousseau",
         "Saint-Antoine","Tenon","Saint-Louis","Hotel Dieu" ), 
lat = c(48.8378796,48.8989884,48.8799187,48.8829237,48.8393,48.8460247,48.8369622,48.841958,48.8485624,48.8663567,48.8749,48.8539489),
lng = c(2.3652543,2.3301387,2.4028936,2.3530628,2.2706000000000586,2.3132671, 2.3401797,2.4066039,2.3824305,2.4015104,2.3654000000000224,2.3477596))
str(hospitals$name)
```

### 2/ Look for closest hospital based on user's position

Let's calculate the distance from user's position to all hospitals. We then order the hospitals according to their distance.  
Below is an example of output with the coordinates (48.86; 2.34) :   

```{r calc_dist}
input <- data.frame(lat = 48.86, lng = 2.34)

for (i in 1:dim(hospitals)[1]) {
        hospitals$dist[i] <- distm(c(input$lng, input$lat), c(hospitals$lng[i], hospitals$lat[i]), fun = distHaversine)
}

calc_dist <- hospitals[order(hospitals$dist)[1],]
calc_dist
```

### 3/ Use speed to calculate time to reach the closest hospital. 

## Map Example

Using this small app, Paris residents may locate easily the closest hospital from their location. 

```{r plot}
df <- data.frame(lat = c(input$lat,calc_dist[1,2]),
                 lng = c(input$lng,calc_dist[1,3]),
                 type = c("departure","hospital"),
                 content = c("Departure",paste("Hopital",calc_dist[1,1])))

hospitalIcon <- makeIcon(
      iconUrl = ifelse(df$type == "hospital",
                       "https://image.flaticon.com/icons/svg/504/504276.svg", 
                       "https://png.pngtree.com/svg/20170505/7b67d2699c.svg"),
      iconWidth = 31*215/230, iconHeight = 31, 
      iconAnchorX = 31*215/230/2, iconAnchorY = 16)

leaflet(data = df) %>%
        addTiles() %>%
        setView(2.34,48.86, zoom = 12) %>%
        addMarkers(lat = ~lat, lng = ~lng, icon = hospitalIcon, popup = ~content)
```

## Further improvements
To increase practicability, we may :   
- use smartphone's geolocation feature to get latitude and longitude coordinates automatically  
- add informations on each hospital (such as areas of expertise, etc.)  
- connect the service with Google maps to deliver a road itinerary to the user 